Supplementary Information: Global patterns of forest autotrophic carbon fluxes

### 2021-02-26 manuscript/manuscript_word.Rmd
small fixes

\newpage
### Abstract
Carbon (C) fixation, allocation, and metabolism by trees set the basis for energy and material flows in forest ecosystems and define their interactions with Earth's changing climate. 
However, while many studies have considered variation in productivity with latitude and climate, we lack a cohesive synthesis on how forest carbon fluxes vary globally with respect to climate and one another. 
Here, we draw upon 1,319 records from the Global Forest Carbon Database (ForC), representing all major forest types and the nine most significant autotrophic carbon fluxes, to comprehensively review how annual C cycling in mature, undisturbed forests varies with latitude and climate on a global scale. 
Across all flux variables analyzed, rates of C cycling decreased continuously with absolute latitude -- a finding that confirms multiple previous studies and contradicts the idea that net primary productivity of temperate forests rivals that of tropical forests. 
C flux variables generally displayed similar trends across latitude and multiple climate variables, with no differences in allocation detected at this global scale.
Temperature variables in general, and mean annual temperature or temperature seasonality in particular, were the single best predictors of C flux, explaining 19 - 71% of variation in the C fluxes analyzed. 
The effects of temperature were modified by moisture availability, with C flux reduced under hot and dry conditions and sometimes under very high precipitation. 
Annual C fluxes increased with growing season length and were also influenced by growing season climate. 
These findings clarify how forest C flux varies with latitude and climate on a global scale. 
In an era when forests will play a critical yet uncertain role in shaping Earth's rapidly changing climate, our synthesis provides a foundation for understanding global patterns in forest C cycling.

>>>>

\newpage
### Abstract
Carbon (C) fixation, allocation, and metabolism by trees set the basis for energy and material flows in forest ecosystems and define their interactions with Earth's changing climate. 
However, while many studies have considered variation in productivity with latitude and climate, we lack a cohesive synthesis on how forest carbon fluxes vary globally with respect to climate and one another. 
Here, we draw upon 1,319 records from the Global Forest Carbon Database (ForC), representing all major forest types and the nine most significant autotrophic carbon fluxes, to comprehensively review how annual C cycling in mature, undisturbed forests varies with latitude and climate on a global scale. 
Across all flux variables analyzed, rates of C cycling decreased continuously with absolute latitude -- a finding that confirms multiple previous studies and contradicts the idea that net primary productivity of temperate forests rivals that of tropical forests. 
C flux variables generally displayed similar trends across latitude and multiple climate variables, with no differences in allocation detected at this global scale.
Temperature variables in general, and mean annual temperature or temperature seasonality in particular, were the best single predictors of C flux, explaining 19 - 71% of variation in the C fluxes analyzed. 
The effects of temperature were modified by moisture availability, with C flux reduced under hot and dry conditions and sometimes under very high precipitation. 
Annual C fluxes increased with growing season length and were also influenced by growing season climate. 
These findings clarify how forest C flux varies with latitude and climate on a global scale. 
In an era when forests will play a critical yet uncertain role in shaping Earth's rapidly changing climate, our synthesis provides a foundation for understanding global patterns in forest C cycling.
